---
title: "Turnover: Bad Pass"
author: "Rainbow Gu"
format: 
  html：
    self-contained: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| message: false
# load package
library(tidyverse)
library(dplyr)
library(ggplot2)
library(grid)
library(png)
```

## Analyzing BOS Turnover through Matches with MIA and GSW
```{r}
#| message: false
# load data containing player's name
player_analyze_results <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/DatafromNBA/player_analyze_result.csv")
player_names <- player_analyze_results|>
  select(player_id,player_name)

# half court graph
courtImg.URL <- "/Users/rainbowgu/Documents/SDS R/2023 Hackathon/nba_court.png"
court <- rasterGrob(readPNG(courtImg.URL),
           width=unit(1,"npc"), height=unit(1,"npc"))

# load all pbp BOS turnover
t0301 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100301.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)
t0302 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100302.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)
t0303 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100303.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)
t0304 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100304.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)
t0305 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100305.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)
t0306 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100306.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)
t0307 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100307.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)

t0401 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100401.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)
t0402 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100402.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)
t0403 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100403.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)
t0404 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100404.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)
t0405 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100405.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)
t0406 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100406.csv")|>
  filter(grepl('Turnover', description), team_id == 1610612738)

# seperate to different opponent matches
pbp_BvM <- rbind(t0301,t0302,t0303, t0304, t0305, t0306, t0307)
pbp_BvG <- rbind(t0401,t0402,t0403, t0404, t0405, t0406)

rm(t0301,t0302,t0303, t0304, t0305, t0306, t0307, t0401,t0402,t0403, t0404, t0405, t0406)
```

#### BOS vs MIA, BOS Turnovers

```{r}
# join corresponding names into the play-by-play data
pbp_BvM_names <- left_join(pbp_BvM, player_names, by = c("player1_id"="player_id"))
pbp_BvM_names <- distinct(pbp_BvM_names)
```

```{r}
#| warning: false
# plot turnovers of BOS players in all seven BOS vs MIA matches
graphBvM_tloc <- pbp_BvM_names |>
  filter(event_type == 5) |>
  mutate(event_type_cate = as.character(event_type)) |>
  mutate(team = gsub("^\\[|\\]$", "", gsub(".*\\[([^]]*)\\].*", "\\1", description))) |>
  mutate(team = gsub("\\s\\d+-\\d+", "", team)) 

ggplot(data = graphBvM_tloc,
  aes(x=locX, y=locY)) +
  annotation_custom(court, -250, 250, -50, 420) +
  geom_point(aes(colour = player_name) )+
  xlim(-250, 250) +
  ylim(-50, 420) +
  labs(title = "BOS vs MIA Total BOS Turnovers, 2022",
       subtitle = "All 7 BOS vs MIA Matches Combined",
       colour = "Players") 
```
Miami's defense is generally weaker therefore they are blocking turnovers in more dangerous zones near the rim.

#### BOS vs GSW, BOS Turnovers

```{r}
# join corresponding names into the play-by-play data
pbp_BvG_names <- left_join(pbp_BvG, player_names, by = c("player1_id"="player_id"))
pbp_BvG_names <- distinct(pbp_BvG_names)
```

```{r}
#| warning: false
# plot turnovers of BOS players in all seven BOS vs GSW matches
graphBvG_tloc <- pbp_BvG_names |>
  filter(event_type == 5) |>
  mutate(event_type_cate = as.character(event_type)) |>
  mutate(team = gsub("^\\[|\\]$", "", gsub(".*\\[([^]]*)\\].*", "\\1", description))) |>
  mutate(team = gsub("\\s\\d+-\\d+", "", team)) 

ggplot(data = graphBvG_tloc,
  aes(x=locX, y=locY)) +
  annotation_custom(court, -250, 250, -50, 420) +
  geom_point(aes(colour = player_name) )+
  xlim(-250, 250) +
  ylim(-50, 420) +
  labs(title = "BOS vs GSW Total BOS Turnovers, 2022",
       subtitle = "All 7 BOS vs GSW Matches Combined",
       colour = "Players") 
```
Golden State Warriors' defense is generally stronger therefore their blocks are more spread out in the court; a stronger tendency to have turnovers resulting in the locX=100 location points to the possible stronger in defense in the left portion of the court near the rim by the GSW.


## Turnovers Analysis

#### Turnover at Each Score
```{r}
#| warning: false
ggplot(pbp_BvM_names, aes(x = home_score)) +
  geom_histogram() +
  labs(title = "Amount of Turnovers at Each Score, BOS vs MIA 2022",
       subtitle = "All 7 BOS vs MIA Matches Combined",
       x = "Home Score",
       y = "Amount of Turnovers") 
```

```{r}
#| warning: false
ggplot(pbp_BvG_names, aes(x = home_score)) +
  geom_histogram() +
  labs(title = "Amount of Turnovers at Each Score, BOS vs GSW 2022",
       subtitle = "All 7 BOS vs GSW Matches Combined",
       x = "Home Score",
       y = "Amount of Turnovers") 
```

#### Turnover Types & Location

```{r}
# renaming different types of turnovers
pbp_all<- rbind(pbp_BvM_names, pbp_BvG_names)
pbp_all <- pbp_all|> 
  filter("event_action_type" != 11, "event_action_type" != 13, "event_action_type" != 36)

pbp_all$event_action_type <- as.character(pbp_all$event_action_type)

pbp_all<- pbp_all|>
  mutate(event_action_type = case_when(
    event_action_type == "1"~ "Bad Pass (steal)",
event_action_type == "2"~ "Lost Ball (steal)",
event_action_type == "4"~ "Traveling",
event_action_type == "6" ~ "Double Dribble",
event_action_type == "11"~ "Shot Clock",
event_action_type == "13"~ "Backcourt",
event_action_type == "36"~ "Illegal Screen Turnover",
event_action_type == "37"~ "Offensive Foul Turnover",
event_action_type == "39"~ "Step Out of Bound",
event_action_type == "40"~ "Out of Bounds Lost Ball",
event_action_type == "45"~ "Out of Bounds Bad Pass",
TRUE ~event_action_type))

# select turnovers by cause
pbp_all_causedT <- pbp_all |>
  filter(!(event_action_type %in% c("Shot Clock", "Backcourt", "Illegal Screen Turnover")))

# plot
graphall_tloc <- pbp_all_causedT |>
  filter(event_type == 5) |>
  mutate(event_type_cate = as.character(event_type)) |>
  mutate(team = gsub("^\\[|\\]$", "", gsub(".*\\[([^]]*)\\].*", "\\1", description))) |>
  mutate(team = gsub("\\s\\d+-\\d+", "", team)) 

ggplot(data = graphall_tloc,
  aes(x=locX, y=locY)) +
  annotation_custom(court, -250, 250, -50, 420) +
  geom_point(aes(colour = event_action_type) )+
  xlim(-250, 250) +
  ylim(-50, 420) +
  labs(title = "All BOS, 2022",
       colour = "Reasons for Turnovers") 
```

#### Turnover Types and Clock Time

```{r}
# changing clock format
pbp_all_causedT <- pbp_all_causedT %>%
  mutate(clock_minutes = as.numeric(substring(clock, 1, 2)) * 60 + as.numeric(substring(clock, 4, 5)))
```

```{r}
# Define the breaks to separate time into five sections
time_breaks <- c(0, 150, 300, 450, 600, 750)

# Create a new categorical variable to represent the time sections
pbp_all_causedT$time_section <- cut(pbp_all_causedT$clock_minutes, breaks = time_breaks,
                                    labels = c("0-150 minutes", "150-300 minutes", "300-450 minutes", "450-600 minutes", "600-750 minutes"),
                                    right = FALSE)

# Convert time_section to a factor to preserve the order of levels in the stacked bar plot
pbp_all_causedT$time_section <- factor(pbp_all_causedT$time_section,
                                       levels = c("0-150 minutes", "150-300 minutes", "300-450 minutes", "450-600 minutes", "600-750 minutes"))

# Create the stacked bar plot with time_section as the stacks
ggplot(pbp_all_causedT, aes(x = time_section, fill = event_action_type)) +
  geom_bar(position = "stack") +
  labs(title = "Turnovers Over Time of All Matches",
       x = "Time Section",
       y = "Turnover Number")
```
Steals are the most direct cause of turnovers.

## BOS Defence

Analysis on which kind of turnovers are more frequent initiated by BOS on other teams
```{r}
#| message: false
# load all play-by-play data of turnovers of the other team
t0301 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100301.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)
t0302 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100302.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)
t0303 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100303.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)
t0304 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100304.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)
t0305 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100305.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)
t0306 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100306.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)
t0307 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100307.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)

t0401 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100401.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)
t0402 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100402.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)
t0403 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100403.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)
t0404 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100404.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)
t0405 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100405.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)
t0406 <- read_csv("/Users/rainbowgu/Documents/SDS R/2023 Hackathon/pbp/g0042100406.csv")|>
  filter(grepl('Turnover', description), !team_id == 1610612738)

# seperate to different opponent matches
pbp_M <- rbind(t0301,t0302,t0303, t0304, t0305, t0306, t0307)
pbp_G <- rbind(t0401,t0402,t0403, t0404, t0405, t0406)

rm(t0301,t0302,t0303, t0304, t0305, t0306, t0307, t0401,t0402,t0403, t0404, t0405, t0406)
```

#### BOS vs MIA, MIA Turnovers
```{r}
# join player names 
pbp_M_names <- left_join(pbp_M, player_names, by = c("player1_id"="player_id"))
pbp_M_names <- distinct(pbp_M_names)
```

```{r}
pbp_M_names$event_action_type <- as.character(pbp_M_names$event_action_type)

pbp_M_names<- pbp_M_names|>
  mutate(event_action_type = case_when(
    event_action_type == "1"~ "Bad Pass (steal)",
event_action_type == "2"~ "Lost Ball (steal)",
event_action_type == "4"~ "Traveling",
event_action_type == "6" ~ "Double Dribble",
event_action_type == "11"~ "Shot Clock",
event_action_type == "15"~ "Offensive Goaltending",
event_action_type == "21"~ "Palming Turnover",
event_action_type == "13"~ "Backcourt",
event_action_type == "36"~ "Illegal Screen Turnover",
event_action_type == "37"~ "Offensive Foul Turnover",
event_action_type == "39"~ "Step Out of Bound",
event_action_type == "40"~ "Out of Bounds Lost Ball",
event_action_type == "45"~ "Out of Bounds Bad Pass",
TRUE ~event_action_type))

pbp_M_causedT <- pbp_M_names |>
  filter(!(event_action_type %in% c("Shot Clock", "Backcourt", "Illegal Screen Turnover")))
```

```{r}
#| warning: false
# plot 
graphM_tloc <- pbp_M_causedT |>
  filter(event_type == 5) |>
  mutate(event_type_cate = as.character(event_type)) |>
  mutate(team = gsub("^\\[|\\]$", "", gsub(".*\\[([^]]*)\\].*", "\\1", description))) |>
  mutate(team = gsub("\\s\\d+-\\d+", "", team)) 

ggplot(data = graphM_tloc,
  aes(x=locX, y=locY)) +
  annotation_custom(court, -250, 250, -50, 420) +
  geom_point(aes(colour = event_action_type) )+
  xlim(-250, 250) +
  ylim(-50, 420) +
  labs(title = "MIA Turnover to BOS, 2022",
      subtitle = "All 7 BOS vs MIA Matches Combined",
       colour = "Turnover Type") 
```

#### BOS vs GSW, GSW Turnovers
```{r}
# join player names 
pbp_G_names <- left_join(pbp_G, player_names, by = c("player1_id"="player_id"))
pbp_G_names <- distinct(pbp_G_names)
```

```{r}
pbp_G_names$event_action_type <- as.character(pbp_G_names$event_action_type)

pbp_G_names<- pbp_G_names|>
  mutate(event_action_type = case_when(
    event_action_type == "1"~ "Bad Pass (steal)",
event_action_type == "2"~ "Lost Ball (steal)",
event_action_type == "4"~ "Traveling",
event_action_type == "6" ~ "Double Dribble",
event_action_type == "11"~ "Shot Clock",
event_action_type == "13"~ "Backcourt",
event_action_type == "15"~ "Offensive Goaltending",
event_action_type == "21"~ "Palming Turnover",
event_action_type == "36"~ "Illegal Screen Turnover",
event_action_type == "37"~ "Offensive Foul Turnover",
event_action_type == "39"~ "Step Out of Bound",
event_action_type == "40"~ "Out of Bounds Lost Ball",
event_action_type == "45"~ "Out of Bounds Bad Pass",
TRUE ~event_action_type))

pbp_G_causedT <- pbp_G_names |>
  filter(!(event_action_type %in% c("Shot Clock", "Backcourt", "Illegal Screen Turnover")))
```

```{r}
#| warning: false
# plot
graphG_tloc <- pbp_G_causedT |>
  filter(event_type == 5) |>
  mutate(event_type_cate = as.character(event_type)) |>
  mutate(team = gsub("^\\[|\\]$", "", gsub(".*\\[([^]]*)\\].*", "\\1", description))) |>
  mutate(team = gsub("\\s\\d+-\\d+", "", team)) 

ggplot(data = graphG_tloc,
  aes(x=locX, y=locY)) +
  annotation_custom(court, -250, 250, -50, 420) +
  geom_point(aes(colour = event_action_type) )+
  xlim(-250, 250) +
  ylim(-50, 420) +
  labs(title = "GSW Turnover to BOS, 2022",
      subtitle = "All 7 BOS vs GSW Matches Combined",
       colour = "Turnover Type") 
```

